### 2021-01-23 paper/intro.tex
Fleshing out Sec 1.1

\end{itemize}
In this paper, we will focus on logical models, as those are compositional,
and align well with existing models of sequential composition.
The heart of the model of~\cite{???} is to add logical preconditions
to events, which are introduced by store (modelling data dependencies)
or conditionals (modelling control dependencies):
  \begin{gather*}
    \IF{q \le r} \THEN z\GETS s \FI
    \\
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1.5em]
        \event{wz1}{(q {\le} r) \land (s{=}1) \mid \DW{z}{1}}{}
      \end{tikzinline}}
  \end{gather*}
and are discharged by being ordered with a read event:
  \begin{gather*}
    r\GETS x\SEMI s\GETS y\SEMI \IF{r\le r} \THEN z\GETS s \FI
    \\
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1.5em]
        \event{rx1}{\DR{x}{1}}{}
        \event{ry1}{\DR{y}{1}}{right=of rx1 }
        \event{wz1}{(s{=}1) \limplies (r {\le} r) \land (s{=}1) \mid \DW{z}{1}}{right=of ry1}
        \po{ry1}{wz1}
      \end{tikzinline}}
  \end{gather*}
Note that there is dependency order from $(\DR{y}{1})$ to $(\DW{z}{1})$
so the precondition for $(\DW{z}{1})$ only has to be satisfied assuming the hypothesis
$(s=1)$. There is no matching order from $(\DR{x}{1})$ to $(\DW{z}{1})$
which is why we do not assume the hypothesis $(r=1)$. The precondition on
$(\DW{z}{1})$ is a tautology, and so can be elided:
  \begin{gather*}
    r\GETS x\SEMI s\GETS y\SEMI \IF{r\le r} \THEN z\GETS s \FI
    \\
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1.5em]
        \event{rx1}{\DR{x}{1}}{}
        \event{ry1}{\DR{y}{1}}{right=of rx1 }
        \event{wz1}{\DW{z}{1}}{right=of ry1}
        \po{ry1}{wz1}
      \end{tikzinline}}
  \end{gather*}
\subsection{Sequential composition}

>>>>

\end{itemize}
In this paper, we will focus on logical models, as those are compositional,
and align well with existing models of sequential composition.
The heart of the model of~\cite{???} is to add logical preconditions
to events, which are introduced by store (modelling data dependencies)
or conditionals (modelling control dependencies):
  \begin{gather*}
    \IF{q \le r} \THEN z\GETS s \FI
    \\
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1.5em]
        \event{wz1}{(q {\le} r) \land (s{=}1) \mid \DW{z}{1}}{}
      \end{tikzinline}}
  \end{gather*}
and are discharged by being ordered with a read event:
  \begin{gather*}
    r\GETS x\SEMI s\GETS y\SEMI \IF{r\le r} \THEN z\GETS s \FI
    \\
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1.5em]
        \event{rx1}{\DR{x}{1}}{}
        \event{ry1}{\DR{y}{1}}{right=of rx1 }
        \event{wz1}{(s{=}1) \limplies (r {\le} r) \land (s{=}1) \mid \DW{z}{1}}{right=of ry1}
        \po{ry1}{wz1}
      \end{tikzinline}}
  \end{gather*}
Note that there is dependency order from $(\DR{y}{1})$ to $(\DW{z}{1})$
so the precondition for $(\DW{z}{1})$ only has to be satisfied assuming the hypothesis
$(s=1)$. There is no matching order from $(\DR{x}{1})$ to $(\DW{z}{1})$
which is why we do not assume the hypothesis $(r=1)$. The precondition on
$(\DW{z}{1})$ is a tautology, and so can be elided:
  \begin{gather*}
    r\GETS x\SEMI s\GETS y\SEMI \IF{r\le r} \THEN z\GETS s \FI
    \\
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1.5em]
        \event{rx1}{\DR{x}{1}}{}
        \event{ry1}{\DR{y}{1}}{right=of rx1 }
        \event{wz1}{\DW{z}{1}}{right=of ry1}
        \po{ry1}{wz1}
      \end{tikzinline}}
  \end{gather*}
While existing models of relaxed memory have detailed treatmenmts of parallel composition,
they pften give sequential composition little attention, either ignoring it altogether,
or treating it operationally with its usual small-step semantics. This paper
investigates how existing models of sequential composition interact with relaxed memory.

\subsection{Sequential composition}
